Title

### 2018-02-06 Latex/Basu_propositions/propositions.tex
Just added a neutral title...you never know...
Some modifications on the presentation

\title{5 slides to convince you that it's endogenous TFP}

@@

Final goods firm (GE)
\begin{align*}
\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) } Y_t(s) =  & K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \\
 & \text{where} \; S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t \\
 &  \; A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma} \\
 &  \; G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots \\
  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
\end{align*}

@@

IT-producing firm (Google)
\begin{align*}
\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -w_t L_{2,t}(s) - R_t K_{2,t}(s)
\end{align*}

@@

A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.

An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today.

$\Psi$ is a final-good-specific exogenous technology process.

@@

TFP consists of an exogenous, common technology process $\eta$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology. 
\end{frame}
%%%%%%%%%%%%%%%%%

>>>>

\title{Title}

@@

Final goods firm $s$ (GE)
\begin{align*}
\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) }  & \sum_{t=0}^{\infty} \beta^t \Big[ P_t^C A_t K_{1,t}(s)^{\alpha_1}L_{1,t}(s)^{\alpha_2}S^{IT}_t(s)^{1-\alpha_1 - \alpha_2} \\
& - W_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \Big] \\
\end{align*}
where
\begin{itemize} 
	\item $A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma}$   
	\item $S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t$
	\item $G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots$
	\item $\sum_{i=1}^{N} \zeta_i = 1$
  \end{itemize}

@@

IT-producing firm (Google)
\begin{align*}
\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -W_t L_{2,t}(s) - R_t K_{2,t}(s)
\end{align*}

@@

\begin{itemize}
\item A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.

\item An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today. 
\end{itemize}

@@

where
\begin{itemize}
	\item $\eta$ is a economy-wide exogenous technology process.
	\item $\Psi$ is a final-good exogenous technology process.
	\item The third element is a spillover from the aggregate stock of IT.
	\end{itemize}
